Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-01 src/tex/ms.tex
Formatting

\begin{table}
    \caption{Events that best constrain $\kappa$, sorted by posterior standard deviation $\sigma_i$.}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

\begin{table}
    \caption{Events that show bimodality in the $\kappa$ posterior tend to have high total masses.}
    \begin{ruledtabular}
        \variable{output/bimodal_events_mass.txt}
    \end{ruledtabular}
    \label{tab:bimodal_events_mass}
\end{table}

@@

\begin{figure}
    \script{corner_GW170818_appendix.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW170818_appendix.pdf}
    \caption{
        Corner plot of GW170818.
    }
    \label{fig:corner_GW170818_appendix}
\end{figure}

>>>>

\begin{table}
    \caption{Events that best constrain $\kappa$, sorted by posterior standard deviation $\sigma_i$. CL is the credible level of $\kappa = 0$.}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

\begin{table}
    \caption{Events that show bimodality in the $\kappa$ posterior tend to have high total masses. CL is the credible level of $\kappa = 0$.}
    \begin{ruledtabular}
        \variable{output/bimodal_events_mass.txt}
    \end{ruledtabular}
    \label{tab:bimodal_events_mass}
\end{table}

@@

\begin{figure}[h]
    \script{corner_GW170818_appendix.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW170818_appendix.pdf}
    \caption{
        Corner plot of GW170818.
    }
    \label{fig:corner_GW170818_appendix}
\end{figure}
